Naming Anonymous JavaScript Functions

### 2011-04-12 papers/splash-wavefront2011/sigplanconf-template.tex
table 6 is updated. section 2 example and figures are updated.

So what do JavaScript developers do in practice?  To get empirical evidence we analyzed the source code of ten well-known JavaScript projects \footnote[1]{We did not perform any preprocess to exclude third-party or repeated files in the provided source code bundles.}. For every project, the total number of functions and the number of functions with an identifier shown in Table~\ref{js-functions}. The average ratio of named functions to all functions is less then 7 percent and, excepting one project {\textit Prototype}, the ratio does not exceed 13 percent. Among all functions only a very limited number of them (116 functions) are defined by the {\small\texttt{Function}} constructor. Our analysis does not include the functions defined dynamically by {\small\texttt{eval}} function or {\small\texttt{new Function()}}; these cases would only make the ratio even smaller.  Therefore, we conclude that a large proportion of JavaScript functions are anonymous.

@@

\lstset{basicstyle=\scriptsize}
\lstset{emph={FOO,BAR},emphstyle=\textit}
\lstdefinelanguage{myLang}
{morekeywords={if, function, var, return, new}}

\begin{lstlisting}[frame=single, language=myLang]
9  var main = function() {         // main<
10   return function() {           // main
11     var foo = new FOO("a");
12     var bar = new BAR("b");
13     var result = op(
14       function(value){          // main/result<
15         return value;
16        });
17   }
18 }();
19 var FOO = function(a) {         // FOO
20   this.a = a;
21 }
22 var BAR = function(b) {         // BAR
23   this.b = b;
24 }
25 var op = function() {           // op<
26   var local;
27   return function(callBack) {   // op
28     local++;
29     return callBack(local);
30   }
31 }();
\end{lstlisting}
\caption{An excerpt of a JavaScript code.}
\label{js-code}
\end{figure}

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.47\textwidth,height=.15\textheight]{pic/chrome-objects.jpg}}
\hfil
\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.47\textwidth,height=.15\textheight]{pic/fbug-objects.jpg}}}
\caption{The screenshot of variables view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
\label{debuggers-objects}
\end{figure*}

@@

\subsection{Missed Constructor Name in Object Summary}
JavaScript doesn't support classes, but objects can be created by constructors ({\small\texttt{new}} followed by a function call). A constructor is a regular JavaScript function. Once the {\small\texttt{new}} keyword is evaluated, an empty object, with the constructor prototype as its prototype, is created, then the new object is bound to {\small\texttt{this}} and the constructor is called. The role of constructor is to initialize the empty object. Unlike class-based object-oriented languages, the structure of object imposed by the constructor may change during the object's lifetime \cite{Richards}, the constructor can still be useful in classify the object.
Debuggers employ this fact and display the constructor name in the object summary to facilitate developer's understanding.

Figure~\ref{js-code} shows an excerpt of a JavaScript program we use to illustrate this issue. We set a breakpoint on line 13 and examine the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}). Two objects assigned to variables {\small\texttt{foo}} and {\small\texttt{bar}} are constructed by two different constructors: {\small\texttt{FOO}} and {\small\texttt{BAR}}. However, Google Chrome debugger shows the general class of {\small\texttt{Object}} as the summary for both objects. The developer has to expand the object nodes to recognize their similarities and differences. Firebug classify objects in the same general class, but includes some of the object properties in the summary. These additional properties may hint the developer about the object structures. {\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 19 and 22 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.

\subsection{Anonymous Function Names in Call-stack View}
The second problem is the call-stack.
To illustrate this, we pause the program (Figure~\ref{js-code}) at line 15 by a breakpoint. Figure~\ref{debuggers-callstack} shows how the program call-stack is displayed in Google Chrome debugger and Firebug. The differences in the number of frames and line numbers between two call-stacks are due to dissimilar event handling implementations in the underlying platforms. Google chrome shows \textit{anonymous} as the name of all functions excepting the first one. Firebug performs better by guessing three function names but it still fails in one case. In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behavior.

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.47\textwidth,height=.13\textheight]{pic/chrome-callstack.jpg}}
\hfil
\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.47\textwidth,height=.13\textheight]{pic/fbug-callstack.jpg}}}
\caption{The screenshot of call-stack view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
\label{debuggers-callstack}
\end{figure*}

@@

\begin{table*}
\centering
\scalebox{0.8}{
  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l |}
  \hline
   Project       & Anonymous &  FBUG NoName   & NoName   & NoShortName &    = FBUG Name     & \texttildelow FBUG Name & Duplicates  & Avgerage      & Longest  \\ 
  \hline 
   Closure       & 8987      &   312(3\%)     & 10       &  51         &    66(0.7\%)         &    8462(94\%)         & 113(1\%)    & 33/35         & 76/101 \\ 
  \hline 
   DoJo          & 15866     &   3362(2\%)    & 390      &  528        &    3067(19\%)        &    9115(57\%)         & 2677(17\%)  & 35/36         & 81/162 \\ 
  \hline 
   ExtJS         & 36533     &   1543(4\%)    & 231      &  631        &    4007(11\%)        &    13572(37\%         & 2573(7\%)   & 22/25         & 65/91  \\ 
  \hline 
   Firebug       & 3018      &   167(5\%)     & 10       &  14         &    397(13\%)         &    2442(80\%)         & 2976(1\%)   & 27/36         & 70/140 \\ 
  \hline 
   jQuery        & 399       &   95(24\%)     & 8        &  9          &    151(38\%)         &    131(33\%)          & 64(16\%)    & 14/18         & 50/65  \\ 
  \hline 
   MochiKit      & 1829      &   202(11\%)    & 16       &  59         &    779(43\%)         &    789(43\%)          & 207(11\%)   & 17/22         & 49/80   \\ 
  \hline 
   MooTools      & 618       &   121(19\%)    & 18       &  30         &    266(43\%)         &    180(29\%)          & 156(25\%)   & 12/14         & 36/73   \\ 
  \hline 
   Prototype     & 442       &   125(28\%)    & 19       &  24         &    38(8\%)           &    272(62\%)          & 89(20\%)    & 23/25         & 55/88    \\ 
  \hline  
   Scriptaculous & 884       &   195(22\%)    & 19       &  25         &    79(8\%)           &    573(65\%)          & 105(12\%)   & 22/27         & 55/132   \\ 
  \hline    
   YUI           & 21424     &   3317(15\%)   & 15       &  212        &    4846(23\%)        &    6962(33\%)         & 2220(10\%)  & 16/37         & 114/145  \\ 
  \hline 
   All           & 90000     &   9439(10\%)   & 736(1\%) &  1583(2\%)  &    13696(15\%)       &    42498(47\%)        & 8264(9\%)   &                &          \\ 
  \hline       
  \end{tabular}
  }
 \label{evaluation} 
\caption{Results of Function Object Consumption. The rows are the projects listed in Appendix 1. First column in  contains the number of anonymous functions in each project. The second column shows the number of functions Firebug could not name. The third column contains the number of functions nameless after applying the static Function Object Consumption (FOC) algorithm;  and the fourth column is the number with only a name for enclosing scopes. The fifth column give the number of times a FOC function name appears twice in a file and sixth and seventh columns give the average and longest name character counts respectively. The last columns have two entries divided by a slash, the first is the local name and the second is the full name.} 
\end{table*}

>>>>

So what do JavaScript developers do in practice?  To get empirical evidence we analyzed the source code of ten well-known JavaScript projects\footnote[2]{We did not perform any preprocess to exclude third-party or repeated files in the provided source code bundles.}. For every project, the total number of functions and the number of functions with an identifier shown in Table~\ref{js-functions}. The average ratio of named functions to all functions is less then 7 percent and, excepting one project {\textit Prototype}, the ratio does not exceed 13 percent. Among all functions only a very limited number of them (116 functions) are defined by the {\small\texttt{Function}} constructor. Our analysis does not include the functions defined dynamically by {\small\texttt{eval}} function or {\small\texttt{new Function()}}; these cases would only make the ratio even smaller.  Therefore, we conclude that a large proportion of JavaScript functions are anonymous.

@@

\lstset{basicstyle=\scriptsize}
\lstset{emph={FOO,BAR}} %,emphstyle=\bf}
\lstdefinelanguage{myLang}
{morekeywords={if, function, var, return, new, this}}

\begin{lstlisting}[frame=single, language=myLang]
9  var main = function() {          // main
10   var foo = new FOO(            
11      function(){                 // main/foo<
12        this.welcome = "Hi!";
13      });
14   var bar = new BAR("GoodBye.");
15   alert(foo.welcome);
16   alert(bar.message);
17 };
18 var FOO = function(){            // FOO<    
19   var instances;
20   return function(initializer){  // FOO
21       instances++;         
22       initializer.apply(this);
23     }
24 }();
25 var BAZ = BAR = function(msg){   // BAR
26   this.message = msg;
27 }
\end{lstlisting}
\caption{An excerpt of a JavaScript code.}
\label{js-code}
\end{figure}

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-objects.jpg}}
\hfil
\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-objects.jpg}}}
\caption{The screenshot of variables view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
\label{debuggers-objects}
\end{figure*}

@@

\subsection{Missed Constructor Name in Object Summary}
JavaScript does not support classes, but objects can be created by constructors ({\small\texttt{new}} followed by a function call). A constructor is a regular JavaScript function. Once the {\small\texttt{new}} keyword is evaluated, an empty object, with the constructor prototype as its prototype, is created, then the new object is bound to {\small\texttt{this}} and the constructor is called. The role of constructor is to initialize the empty object. Unlike class-based object-oriented languages, the structure of object imposed by the constructor may change during the object's lifetime \cite{Richards}, the constructor can still be useful in classify the object.
Debuggers employ this fact and display the constructor name in the object summary to facilitate developer's understanding.

Figure~\ref{js-code} shows an excerpt of a JavaScript program we use to illustrate this issue. We set a breakpoint on line 15 and examine the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}). Two objects assigned to variables {\small\texttt{foo}} and {\small\texttt{bar}} are constructed by two different constructors: {\small\texttt{FOO}} and {\small\texttt{BAR}}. However, Google Chrome debugger shows the general class of {\small\texttt{Object}} for {\small\texttt{foo}} and the {\small\texttt{BAZ.BAR}} class for {\small\texttt{bar}} as their summaries. The first class is very general and the second one is misleading. The developer has to expand the object nodes to recognize their similarities and differences. Firebug classify both objects in the general {\small\texttt{Object}} class, but includes some of the object properties in the summary. These additional properties may hint the developer about the object structures. {\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 20 and 25 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.

\subsection{Anonymous Function Names in Call-stack View}
The second problem is the call-stack.
To illustrate this, we pause the program (Figure~\ref{js-code}) at line 12 by a breakpoint. Figure~\ref{debuggers-callstack} shows how the program call-stack is displayed in Google Chrome debugger and Firebug. The differences in the number of frames and line numbers between two call-stacks are due to dissimilar event handling implementations in the underlying platforms. Among three last functions in the call stack, Google Chrome only shows the name of one of them({\small\texttt{main}}) correctly. For the second function (line 22), it shows \textit{anonymous}, and for the third function (line 12), it gives a wrong name, {\small\texttt{foo}}. Firebug performs better by guessing two function names correctly, but it still fails in one case. It shows {\small\texttt{main}} as the name of last function(line 12) which is the name of its enclosing function.
In these cases, the information provided by debugger is useless and the developer has to locate the function source to understand or recall the function behavior.

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-callstack.jpg}}
\hfil
\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-callstack.jpg}}}
\caption{The screenshot of call-stack view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
\label{debuggers-callstack}
\end{figure*}

@@

\begin{table*}
\centering
\scalebox{0.8}{
  \begin{tabular}{ | l | l | l | l | l | l | l | l | l | l |}
  \hline
\multirow{2}{*}{Project} & \multicolumn{4}{|c|}{Anonymous Functions By} &         \multicolumn{3}{|c|}{Quality}               & \multicolumn{2}{|c|}{Local/Full Length}  \\ 
  \cline{2-10}
                 & Developer &   Firebug      & FOC-Local & FOC-Full  &    = FBUG Name     & \texttildelow FBUG Name & Duplicates  & Avgerage      & Longest  \\ 
  \hline 
   Closure       & 8987      &   312(3\%)     & 51        & 10        &    66(0.7\%)         &    8462(94\%)         & 113(1\%)    & 33/35         & 76/101 \\ 
  \hline 
   DoJo          & 15866     &   3362(21\%)    & 528       & 390       &    3067(19\%)        &    9115(57\%)         & 2677(17\%)  & 35/36         & 81/162 \\ 
  \hline 
   ExtJS         & 36533     &   1543(4\%)    & 631       & 231       &    4007(11\%)        &    13572(37\%         & 2573(7\%)   & 22/25         & 65/91  \\ 
  \hline 
   Firebug       & 3018      &   167(5\%)     & 14        & 10        &    397(13\%)         &    2442(80\%)         & 2976(1\%)   & 27/36         & 70/140 \\ 
  \hline  
   jQuery        & 399       &   95(24\%)     & 9         & 8         &    151(38\%)         &    131(33\%)          & 64(16\%)    & 14/18         & 50/65  \\ 
  \hline  
   MochiKit      & 1829      &   202(11\%)    & 59        & 16        &    779(43\%)         &    789(43\%)          & 207(11\%)   & 17/22         & 49/80   \\ 
  \hline 
   MooTools      & 618       &   121(19\%)    & 30        & 18        &    266(43\%)         &    180(29\%)          & 156(25\%)   & 12/14         & 36/73   \\ 
  \hline 
   Prototype     & 442       &   125(28\%)    & 24        & 19        &    38(8\%)           &    272(62\%)          & 89(20\%)    & 23/25         & 55/88    \\ 
  \hline  
   Scriptaculous & 884       &   195(22\%)    & 25        & 19        &    79(8\%)           &    573(65\%)          & 105(12\%)   & 22/27         & 55/132   \\ 
  \hline    
   YUI           & 21424     &   3317(15\%)   & 212       & 15        &    4846(23\%)        &    6962(33\%)         & 2220(10\%)  & 16/37         & 114/145  \\ 
  \hline 
   All           & 90000     &   9439(10\%)   & 1583(2\%) & 736(1\%)  &    13696(15\%)       &    42498(47\%)        & 8264(9\%)   & N/A            & N/A         \\ 
  \hline       
  \end{tabular}
  }
 \label{evaluation} 
\caption{Results of Function Object Consumption. The rows are the projects listed in Appendix 1. First column in  contains the number of anonymous functions in each project. The second column shows the number of functions Firebug could not name. The third column contains the number of functions nameless after applying the static Function Object Consumption (FOC) algorithm;  and the fourth column is the number with only a name for enclosing scopes. The fifth column give the number of times a FOC function name appears twice in a file and sixth and seventh columns give the average and longest name character counts respectively. The last columns have two entries divided by a slash, the first is the local name and the second is the full name.} 
\end{table*}
